Reproducible Summary Tables with gtsummary

### 2020-12-09 RJtemplate_gtsummary_submission.tex

>>>>

\hypertarget{tbl_summary}{%
\subsection{\texorpdfstring{\texttt{tbl\_summary()}}{tbl\_summary()}}\label{tbl_summary}}

% code for basic tbl_summary()
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tbl\_summary\_}\DecValTok{1}\NormalTok{ <{-}}
\StringTok{  }\NormalTok{trial }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{select}\NormalTok{(age, grade, response, trt) }\OperatorTok{\%>\%}
\StringTok{  }\KeywordTok{tbl\_summary}\NormalTok{(}\DataTypeTok{by =}\NormalTok{ trt)}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl_svysummary}{%
\subsection{\texorpdfstring{\texttt{tbl\_svysummary()}}{tbl\_svysummary()}}\label{tbl_svysummary}}

\hypertarget{tbl_cross}{%
\subsection{\texorpdfstring{\texttt{tbl\_cross()}}{tbl\_cross()}}\label{tbl_cross}}

\hypertarget{tbl_survfit}{%
\subsection{\texorpdfstring{\texttt{tbl\_survfit()}}{tbl\_survfit()}}\label{tbl_survfit}}

\hypertarget{customization}{%
\subsection{Customization}\label{customization}}

\hypertarget{model-summaries}{%
\section{Model Summaries}\label{model-summaries}}

\hypertarget{tbl_regression}{%
\subsection{\texorpdfstring{\texttt{tbl\_regression()}}{tbl\_regression()}}\label{tbl_regression}}

\hypertarget{tbl_uvregression}{%
\subsection{\texorpdfstring{\texttt{tbl\_uvregression()}}{tbl\_uvregression()}}\label{tbl_uvregression}}

\hypertarget{in-line-reporting}{%
\section{In-line Reporting}\label{in-line-reporting}}

\hypertarget{merging-and-stacking}{%
\section{Merging and Stacking}\label{merging-and-stacking}}

\hypertarget{themes}{%
\section{Themes}\label{themes}}

\hypertarget{print-engines}{%
\section{Print Engines}\label{print-engines}}
